\documentclass[11pt,a4paper]{moderncv}
\usepackage[margin=0.40in, top=0.2in,bottom=0.3in]{geometry}
\usepackage{multicol}           %% allows to create more than two columns
\usepackage{array}              %% for adjusting column widths in table
\usepackage{color}
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}


\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\setlength{\parindent}{0pt}	%% used for setting the no indentation at the beginning of paras

\setlist{nosep}
\pagenumbering{gobble}

% modern themes
\moderncvstyle{banking}
\moderncvcolor{blue}
\moderncvicons{awesome}
\definecolor{titleblue}{RGB}{20,20,100}

\newcommand{\experience}[4]{
  \vspace{0.1cm}
\item \textbf{\large{#1}} \textit{#2}\hfill\textit{#3}
  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{0em} #4
  \end{itemize}
}

\newcommand{\experiencetwo}[4]{
  \vspace{0.1cm}
\item \textbf{\large{#1}} \hfill\textit{#3}\\\textit{#2}
  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{0em} #4
  \end{itemize}
}


\newcommand{\education}[5]{
\item[] \textbf{\large{#1 :}} #2 - \emph{#3: \textbf{#4}} \hfill\textit{#5}
}


%% Personal data
\firstname{Vaibhav}
\familyname{Agarwal}
\address{Computer Science and Engineering}{IIT Kharagpur} 
\email{vaiagarwal96@gmail.com}
\extrainfo{vaiagarwal96@iitkgp.ac.in}
\extrainfo{\emailsymbol\emaillink{vaiagarwal96@iitkgp.ac.in}}
\social[github]{VaibhavAgarwalVA}
\social[linkedin]{VaibhavAgarwalVA}
\homepage{http://cse.iitkgp.ac.in/~vaibhavagarwal/}
\begin{document}
\maketitle
\vspace{-1cm}
\section*{Educational Qualifications}
\begin{itemize}
  \setlength\itemsep{0.2cm}
  \education{Bachelor of Technology}{Indian Institute of Technology Kharagpur}{CGPA}{8.6/10.0}{July'14-Present}
  \education{Senior Secondary - CBSE}{Mahatma Hansraj Modern School, Jhansi}{Overall percentage}{95.4\%}{2014}
  \education{Secondary - ICSE}{Christ the King College, Jhansi}{Overall percentage}{94\%}{2012}
\end{itemize}

\section*{Interests}
\begin{tabular}{L{6.5cm} L{4cm} L{3.4cm} l}
  Algorithms and Graph Theory & Data Analytics & Networks &
  Artificial Intelligence \\
\end{tabular}

\vspace{-0.1cm}
\section*{Projects}
\begin{itemize}
  \setlength\itemsep{0.5em}

  \experiencetwo{Positioning System using Bipartite Matching and Voronoi Diagrams}{Indian Institute of Technology Kharagpur, under Prof. Jayanta Mukhopadhyay}{May'2016-July'2016}{
   \item Created a positioning module for humanoid robots using computational geometry concepts of Voronoi Cells and Delaunay Triangulations. Also created a role matching module which uses maximum bipartite matching (Hungarian Algorithm) to allot the generated positions to suitable bots dynamically.  
  \item Integrated successfully. Increased the time efficiency of the code
    by 30\% of the previous implementation, using constant memory. 
  \item The team (including me) participated in 3D Simulation League at RoboCup 2016, Germany.
  }
  
  \experiencetwo{Path Planning module for differential drive robots}{Indian Institute of Technology Kharagpur, under Prof. Jayanta Mukhopadhyay}{May'2015-July'2015}{
  \item Created a path planner for differential drive soccer playing robots 
    using Dynamic Window Algorithm.
  \item Obtained successful results, decreasing the slip parameter to less
    than 1\%.  
  \item The implementation was successfully integrated and the team won the 
    Bronze medal for IIT Kharagpur at FIRA 2015, South Korea.
  }

  \experience{Data extraction from a 2-D plot}{OpenSoft competition, IIT Kharagpur}{Feb'2016-Mar'2016}{
  \item Created a module to extract graph information from a plot and create the corresponding data table using OpenCV and Tesseract.
  \item The implementation was successful in more than 80\% of the cases, including dashed lines and discontinued plots. The extraction module was also used to extract out the legend box from the plot.
  }

  \experience{Line follower robot}{Robotics workshop at IIT Kharagpur}{Dec'2014}{
  \item Attended a workshop organised by IEEE and Technology Robotix Society, IIT Kharagpur aimed to create an autonomous line follower robot.
  \item Worked on techniques to build the robot and subsequently, coded the algorithm using DFS traversal to cover the entire grid of lines, using Atmel Studio.
  }

  \experience{Back-end development of Online Game}{Kharagpur Game Theory Society}{Jan'16-Mar'16}{
  \item Contributed to the development of an online game for a flagship contest of KGTS, IIT Kharagpur.
  \item Created modules in php using CodeIgniter framework.
  \item The game witnessed a participation of over 1000 participants from IIT Kharagpur, Delhi University and IIM Rohtak in a 2-day event.
  }

  \experience{Online sales portal}{Software Project, Prof. Partha Pratim Das, IIT Kharagpur}{Mar'2016}{
  \item Created a software in Java which allows users to buy and sell items to different users.
  \item The user can perform administrative roles on his profile and history log, as well as interact with other users through messaging.
  \item Awarded with an "Exceptional" grade in the project work.
  }

\end{itemize}

\vspace{-0.1cm}
\section*{Achievements and Scholarships}
\begin{itemize}
  \setlength\itemsep{0.5em}
\item All India Rank \textbf{217} in Joint Entrance Exam (JEE) Advanced
2014 \textit{among 150,000 candidates}.             \hfill \textit{2014}
\item All India Percentile \textbf{99.99} in Joint Entrance Exam (JEE) Mains 2014 \textit{among 1.5 million candidates}.              \hfill \textit{2014}
\item \textbf{ACM ICPC Asia Amritapuri Regional} Finalist.             \hfill \textit{2015}
\item \textbf{Bronze} winning team member at \textbf{Federation of International Robosoccer Association, South Korea}. \hfill \textit{2015}
\item \textbf{Represented} IIT Kharagpur in \textbf{RoboCup 2016} held in \textbf{Leipzig, Germany}.      \hfill \textit{2016}
\item Kishore Vaigyanik Protsahan Yojana (KVPY) Scholar, Dept of Science and Technology, Govt of India.
  \hfill \textit{2013}
\item National Talent Search (NTSE) Scholarship awardee, by NCERT, Govt of India. \hfill \textit{2010}
\item \textbf{National top 300} in National Standard Examination in Physics and Chemistry. \hfill \textit{2013-14}
\item \textbf{Aditya Birla Group Scholarship} shortlist, amongst \textbf{top 32 IIT freshmen}.      \hfill \textit{2014}
\item Goralal Syngal Scholarship at IIT Kharagpur for \textbf{outstanding academic achievements}.\hfill \textit{2014-15}

\end{itemize}


\section*{Work and Volunteer Experience}
\begin{itemize}
  \setlength\itemsep{0.5em}

  \experience{Algorithmic Game Theory Society, Head}{IIT Kharagpur}{Jan'16-Present}{
  \item	Organise and deliver classes to freshers and sophomores interested in algorithmic game theory. 
  \item	Provided questions and game design to the parent team of Kharagpur Game Theory Society, for its flagship contests Nashify 2015 and 2016; Both events saw the participation of over 200 participants from IIT Kharagpur.
  }
    
  \experience{Image Processing Workshop, Mentor}{Organised by IEEE and Texas Instruments}{Dec'2015}{
  \item Mentored a batch of more than 50 freshers in the image processing workshop.
  \item Taught the freshmen basic image processing algorithms and techniques.
  }

  \experience{Secretary}{Code Club, IIT Kharagpur}{July'14-Present}{
  \item	Problem setter and tester at CodeNites, the fortnightly programming contest in IIT Kharagpur.
  \item	Conducted algorithms and data structures class for freshers. Over 100 students attended the 15-day class.
  \item Organised Bitwise 2016, which saw the participation of over 1000 participants from across the globe.
  }

  \experience{Case Study Team, Sub Head}{Meghnad Saha Hall, IIT Kharagpur}{Jan'16-Present}{
  \item Participated in the inter-hall Case Study competition 2016 and won the First prize.
  \item Suggested a present scenario and future directives to tackle the problem statement using SWOT analysis.
  }

\end{itemize}

\section*{Technical Skills}
\begin{tabular}{L{0.05cm} L{5cm} l}
  &Programming Languages      &C/C++, Java, Python, C\#, PHP, x86 Assembly\\
  &Operating Systems	        &Ubuntu, Microsoft Windows\\
  &Utilities                  &Git, GDB, Shell, \LaTeX, Docker\\
\end{tabular}

\section*{Relevant Courses}
% \begin{tabular}{L{0.05cm} L{6.5cm} L{7.0cm} L{8cm} L{8cm} L{12cm}}
\begin{tabular}{L{7.2cm} L{6.0cm} L{5.6cm}l}
  Algorithms 1 & Algorithms 2 * &
  Graph Theory * \\  Software Engineering & Automata Theory &  Compilers * \\
  Computer Organization *  & Discrete Structures & Data Structures\\
  Switching Circuits and Logic Design &
  Probability and Statistics & \textit{* denotes ongoing courses} \\
\end{tabular}

\section*{Miscellaneous}
\begin{itemize}
  \item Got sponsorship to attend RoboCup 2016 Symposium at Leipzig, Germany from IIT Kharagpur.
  \item Occasional contributor to Open Source and self projects on Github.
    \url{https://github.com/VaibhavAgarwalVA}
  \item CodeChef profile - \url{https://codechef.com/users/infiniticoder}.
  \item Vice Captain of the Maths Olympiad team of MS Hall. Winner of Open IIT Maths Olympiad 2015 and Freshers Maths Olympiad 2014 organised by Technology Students' Gymkhana, IIT Kharagpur.
  \item Likes to read, observe and innovate.
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "twopage"
%%% End:

